Interisland movements of woodland caribou in Newfoundland

### 2020-02-21 paper/manuscript.Rmd
edits

## Individual variation 
In total, 3 of 29 collared female caribou swam between islands in the Fogo
archipelago. These swimming events were relatively frequent, on average occuring
once every 24 <!--double check--> days during ice-free seasons. However, we
identified zero swimming events for the other 26 collared females. It remains
unclear why this behaviour is seemingly common among 10% of our marked
population, while 90% never engaged in it. Our initial direct observation of
swimming was an adult male, but as we only have GPS data for females, we are
unable to make conclusions on the prevalence of this behaviour among male
caribou. It is theoretically possible that these other females moved rapidly
back and forth between islands within the 2 hour fix rate of our GPS collars,
which we would be unable to detect. We consider this highly unlikely given the
range of residency times for caribou on any given island (min - max: XX - XX).
<!-- What is the typical residency time? Is this a true statement or am I just making this up? -->

>>>>

## Individual variation 
In total, 3 of 29 collared female caribou swam between islands in the Fogo
archipelago. These swimming events were relatively frequent, on average occuring
once every 24 <!--double check--> days during ice-free seasons. However, despite relatively frequent swimming events for these three individuals, we were unable to
identify any swimming events for the other 26 collared females. It remains
unclear why ocean swimming is relatively common among ~10% of our marked
population, while the other 90% never swam. A potential explanation is the Our initial direct observation of
swimming was an adult male, but as we only have GPS data for females, we are
unable to make conclusions on the prevalence of this behaviour among male
caribou. It is theoretically possible that these other females moved rapidly
back and forth between islands within the 2 hour fix rate of our GPS collars,
which we would be unable to detect. We consider this highly unlikely given the
range of residency times for caribou on any given island (min - max: XX - XX).
<!-- What is the typical residency time? Is this a true statement or am I just making this up? -->
